### 2014-03-25 Paper_Markdown.Rmd
Started editing again.  main change was to create both parallelized and non-parallelized instances of the program.

```{r Fig3SiteMDS, fig.width=7, fig.height=6, fig.cap='Figure: North American site MDS scores', echo=FALSE, message=FALSE, warning=FALSE}

mds <- data.frame(pol.mds$points,
                  non.ana = factor(min.diss > 0.48))

>>>>

```{r Fig3SiteMDS, fig.width=7, fig.height=6, fig.cap='Figure: North American site MDS scores', echo=FALSE, message=FALSE, warning=FALSE}
X
mds <- data.frame(pol.mds$points,
                  non.ana = factor(min.diss > 0.48))
